### 2009-07-09 docs/architecture/architecture.tex
add a figure showing different data centerings

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing where the data in this
  \fab\ is defined.
\item {\tt pbx} is a \boxtype\ that extends {\tt bx} to include
  any ghostcells
\item {\tt ibx}
\item {\tt nc} is the number of components (how many variables at  
  each grid location).
\item {\tt p} is a pointer to the data.
\end{itemize}

Note that alternate datatypes exist for data that is not
double-precision.

Also note that all state data is stored in a four-dimensional array,
{\tt (nx,ny,nz,nc)} in size, regardless of the dimensionality of the
problem.  For 2D problems, {\tt nz=1}.

@@

@@

@@

>>>>

\subsubsection{Common Operations on a \boxtype}

For a \boxtype\ declared as:
\begin{verbatim}
  type(box) :: mybox
\end{verbatim}

\item {\tt lo = lwb(mybox)} returns an array, {\tt lo(dm)}, with
     the box lower bounds

\item {\tt hi = upb(mybox)} returns an array, {\tt hi(dm)}, with
     the box lower bounds

@@

\noindent Here:
\begin{itemize}
\item {\tt dim} is the dimensionality of the data
\item {\tt bx} is a \boxtype\ describing where the data in this
  \fab\ is defined.
\item {\tt pbx} is a \boxtype\ that extends {\tt bx} to include
  any ghostcells
\item {\tt ibx}
\item {\tt nc} is the number of components (how many variables at  
  each grid location).
\item {\tt p} is a pointer to the data, in this case double precision
  ({\tt kind=dp\_t}).  Other \fab\ types exists for other Fortran
  data types.
\end{itemize}

Note that all state data is stored in a four-dimensional array,
{\tt (nx,ny,nz,nc)} in size, regardless of the dimensionality of the
problem.  For 2D problems, {\tt nz=1}.

In MAESTRO, we don't usually deal with \fab s alone, but rather
through \multifab s, described next.

@@

\begin{figure}[t]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings: (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in both the $x$- and $y$-directions.}
\end{figure}

@@

\subsection{{\tt probin\_module}}

@@

\section{Visualization / Analysis}
